Approximate \revised{Translational} Building Blocks for Image Parsing and Synthesis

### 2014-11-06 Paper/paper.tex
paper update

We replace structural priors by the assumption of coherently mapped building blocks, which are related by a common transformation and residual distortions. We discover such structures by relating co-occurance maps of images features using a spectral embedding, which draws its robustness out of the ability to use the whole \revised{4D (chris: this is in the old paper and I do not understand it now)} matching information in a single optimization for discovering coherently mapped pieces. We evaluate our method on a large benchmark data set of facade images. In comparison to previous methods, both with \cite{Wu2010DL} and without structural priors \cite{LIPMANsig2010,Liu2013GRASP}, we obtain a significant improvement.

@@

In summary, the main contribution of this paper is a new approach for discovering \emph{approximate \revised{translational} building blocks} in unreliable data. We develop the idea in the context of an automatic image parsing technique that discovers translational building blocks, and outperforms previous methods in this task. We demonstrate the utility of the discovered building blocks and their geometric relations by applying it to image synthesis, where we can get improvements over unguided methods without sacrificing the fully automatic mode of operation.

@@

\textbf{Symmetry detection} has drawn a considerable amount of interests in both the 2D \cite{Lee2009SR,Wu2010DL} and 3D case \cite{Mitra2006PAA,Pauly2008,LIPMANsig2010,HuangMesh2013}. Most methods perform certain voting, either in the feature space or in the transformation space, and detect symmetries at the local maximums of the vote density. A key for successful detection is to get a good signal to noise ratio for the true repetitions. In feature space, this can be addressed as a feature selection problem. Both global \cite{Wang2008Factor,Agrawal2012RI,Bokeloh2009SD} and local \cite{Leung1996} searches are proposed to find more reliable features, sometimes even constellation of features \cite{Liu2013GRASP}.
%
However, matching is still challenging under strong appearance variation. This problem is partially overcome by voting in the transformation space \cite{Hays2006Texture,Mitra2006PAA}, where spatial mappings between pairwise-matched features are aggregated to amplify the true repetition signal. For lattice-like patterns, detection can be further improved by assuming regular (or near-regular) transformations \cite{Pauly2008,Wu2010DL,Zhao2011TS,Tai2012PF}, see \cite{Lin2006Eva} for a survey.
%
However, this also prohibits detection of irregular patterns. Our method was inspired by the \emph{microtile} decomposition of Kalojanov et al.~\shortcite{KALOJANOVsgp2012}, which characterize generically placed building blocks. However, their method is strictly limited to exact data; even small, numerical errors already cause instability.

We also draw inspiration from Lipman et al.~\cite{LIPMANsig2010}, who use spectral clustering to find cliques of pairwise corresponding points in noisy data. Our method extends their model towards cliques of coherently mapped build blocks (rather than points), which improves detection performance.

\textbf{Visual pattern mining:} Supervised, discriminatively trained models (such as \cite{Felzenszwalb2010DPM}) have demonstrated impressive capabilities in structuring images. Unsupervised pattern mining has been addressed by Singh et al.~\shortcite{SINGHeccv2012}. The original method still requires a large background (negative) training set. In our paper, we adapt the basic technique for mining patterns in a single image, where building-block priors provide additional constraints. More recently, great effort has also been made towards fa{\c{c}}ade parsing. Numerous methods \cite{Teboul2011SG,Martinovic2012AT,Bao2013PF} have been proposed to extract semantic layout of building fa{\c{c}}ades. Convincing images can be later synthesized, using methods such as \cite{Dai2013Facade}. However these methods only work on fa{\c{c}}ade and need either supervised learning or manual interaction, while we aim at a fully unsupervised method that generalizes well for a broader range of subjects, so it could directly used to improve existing image synthesis and editing approaches. 
Cheng et al.~\cite{Cheng2010RepFinder} propose a method for finding repetitive image content for use in synthesis applciations. However, in that method, both the mining and synthesis steps again need considerable human supervision. Landes et al.~\cite{Landes2009} find repetitive patterns and re-arrange them in the synthesis image. Here, the use of a simple feature comparison (SIFT with a Euclidean metric) limits the scope of the automatic detections.

\textbf{Texture synthesis} has received a lot of attention in computer graphics, see \cite{Wei2009STAR} for a comprehensive survey. In order to overcome the limitations of the Markov Random Field (MRF) model, various forms of guidance have been employed, for example, using an additional image layer with user annotations \cite{Hertzmann2001IA} or on-the-fly user interaction ~\cite{Barnes2009,Hu2013PPI}. Automating the creation of guidance map is still an on-going research topics, with some success in low level feature maps. For example, Lefebvre and Hoppe~\shortcite{Lefebvre2006ATS} use distance transforms on feature maps to guide the synthesis of high-quality textures with pronounced meso-structure. However, the feature transform cannot structure complex images beyond textures. Rosenberger et al.~\shortcite{Rosenberger2009LSS} extend the idea to irregular textures with non-stationary statistics, such as aged or weathered surfaces. Dishler et al.~\shortcite{Dischler2002} use ``texture particles'' as landmarks, similar to our guidance scheme; however, only textures (with some meso-structure) are synthesized due to limitations in the detection stage. Tiling grammars have been recently employed to guide the placement of discrete elements~\cite{Ma2011DET,Ma2013DET}, however our method handles image data, such as pixels color and class labels, rather than discrete elements. Our application is also related to image retargeting, recomposition and inpainting. Along this direction, various methods have been experimented to avoid local optimal solutions results from the MRFs model. For example, \cite{Simakov2008SV} uses bidirectional matching and a gradual resizing procedure for retain the image structure in retargeting (especially for image shrinking); \cite{Pritch09ICCV,He2012PO} studied pixel offset, and use graph cut to find the optimal pixel assignment for the output image that produces a smooth offset field. Nonetheless, these methods all operate on image pixels, hence can not eliminate structural artefacts. An exception is \cite{Wu2010SS}, which use deformable lattice to retain structure during image resizing. However their method is restricted to images has a global repetition (such as lattice), and is difficult to be used for recomposition. In this paper we will show using additional \revised{building blocks} knowledge is able to improve the performance of the conventional pixel based MRF methods.

@@

\textbf{Learning:} We train a linear support vector for each cluster in one-versus-all fashion: One of the clusters provides the positive training set and all others the negative set. Doing this for each cluster yields weight vectors $\bv{w}_i$ that characterize each feature cluster.

\textbf{Detection:} The detection step updates the dictionary using sliding window detection. For each $8\times 8$-patch of HOG-cells in the image, it computes:
%
\begin{equation}
m_{\textbf{t}_i}(\textbf{x}) = \exp\left(-||\textbf{w}_i\cdot(HOG(\textbf{t}_i) - HOG(\textbf{x}))||_2 \right),
\label{eq:finalMatching}
\end{equation}
%
where $HOG(\bv{x})$ denotes the local $64^2$ pixel HOG patch for image position $\bv{x}$ and median template $\bv{t}_i$, respectively. The result is one \emph{co-occurance map} for each feature cluster $\bv{t}_i$. Such a map is a scalar image that for each HOG-cell indicates the strength of the match with $\bv{t}_i$; Figure \ref{fig:DL1} compare the co-occurrence maps before and after the learning process.

\textbf{Rebuilding the dictionary:} For the next iteration, we rebuild the the dictionary by using non-maxima suppression ($\frac{1}{4}$ patch size) on the co-occurance maps. Matches with a score below a threshold of $\theta = 0.5$ are removed to avoid spurious local maxima. The threshold is intentionally set to a relative low value to allow considerable appearance variation in the repetitive objects. The whole pipeline is then iterated to refine the results.

@@

For an $w \times h$ input image, let $\domain = [0,w/8] \times [0, h/8]$ denote the domain of the HOG-cell representation of the image. We consider a group of \emph{admissible transformations} $\allTransf$ that can be used to move image content (used to relate instances of building blocks). We restrict $\allTransf$ to translations in this paper, for simplicity. Extensions to larger groups (such as similarity transforms, homographies) are possible but left for future work.

@@

\begin{algorithm}
\caption{Image Parising}\label{alg:ImageParsing}
\begin{algorithmic}[1]
\Require{Input image $I$, Maximum number of iteration $N$ for dictionary initialization, maximum number of iteration $M$ for discriminative learning}
\For{$i \gets 1 \textrm{ to } N$}

@@

\subsubsection{Co-occurance clustering}

In order to address problem (i), finding the transformations, we consider the collection of all 2D slices of the 4D matching function $m$. Consistently with Equation~\ref{eq:finalMatching}, we define the \emph{co-occurance map} of the feature at point $\vecp \in \domain$ as:
%
\begin{equation}
m_{\vecp}(\vecx) := m(\vecp, \vecx)
\label{eq:corr-map}
\end{equation}
%
This is a simple scalar image, depiciting the spatially-varying strength of match against the feature at image position $\vecp$. If two image positions $\vecp$ and $\vecq$ are part of the same building block, they will have related co-occurrance maps $\corrMap_\vecp,\corrMap_\vecq$ (Figure~\ref{fig:coOccurranceDetection}). The following holds for any point in any of the instances of the building blocks, which makes the method particularly robust:
In absence of noise, the co-occurance maps of all points on the same building block type will be exact translationally shifted copies of each other. Even in the noisy case, we can expect the images to still resemble each other. Because we obtain an image for every point on a building block, we have a large amount of information we can integrate to even detect weak signals in very noisy and unreliable correspondence information: By comparing the whole image we are able to drastically reduce the noise of the pixel-wise matching function, and clustering the space of all such images can further detect weak patterns. This is the key property for the robustness of our method, and explains the favorable performance in practice. Unlike previous transformation voting methods~\cite{Mitra2006PAA}, transformations from different instances do not mix and pollute the voting space, and spectral methods are improved by being able to utilize all instance information simultaneously rather than corresponding point orbits.

To find clusters of such related co-occurance maps, we employ a spectral clustering algorithm, which has a global view of all pairwise relations. We first compute the normalized cross-correlation (denoted by $\otimes$) of all pairs of co-occurrance maps $\corrMap_{p},\corrMap_{q}$ to find and score their best translational alignment. We then build a dissimilarity matrix $\textbf{D}$ where
%
\begin{equation}
\textbf{d}_{p, q} = \textbf{d}_{p, q} = 1 - \corrMap_{p} \otimes \corrMap_{q} \text{ for all } p,q \in K\text{.}
\label{eq:distanceMatrix}
\end{equation}
%
We now reconstruct a low dimensional embedding using classical (spectral) multidimensional scaling, where similar co-occurrence maps are located close to each other. We then extract modes of this embedding using meanshift clustering (with bandwidth 0.5), which result in $Q$ clusters ($Q \leq K$). We only keep the median point in each cluster to represent the modes in an outlier-robust way. Figure \ref{fig:SpectralClustering} shows an example of spectral clustering based on co-occurrence maps and compare the result with spectral clustering based on HoG feature distance. By spectral embedding the co-occurrence maps (right), our algorithm is able to group together parts of the same type of building block. For example the word A and B have very different visual appearance but are highly correlated by their co-occurrence maps. In contrast, spectral embedding the HoG features (middle) will falsely group visually similar patches that do not belong the same building block, for example, word B and C.

Each cluster in the embedding is essentially a clique for distributing instances of a particular type of building blocks. We denote the cliques as $\bar{\corrMap}_1,...\bar{\corrMap}_Q$. They are encoded as binary masks in image space by applying the same thresholding and non-maxima supression to the co-occurrence maps as described in the second last paragraph of Section \ref{sec:IterativeDL}. In these masks, one pixel is set to one for each local maxima and all other cells have value zero. Knowing the cliques, we next identify the exact shapes of each building block instance.

Finally, we can easily integrate the learned dictionaries computed in step 1 by computing and embedding the co-occurance maps only for the dictionary entries rather than for all image features. This dramatically reduces the costs for spectral embedding over a naive all-pairs approach and additionally profits from the pre-sharpened detectors.

%It is important to note that our clustering is also very different from symmetry factored embedding~\cite{LIPMANsig2010}, which considers only equality of points, not of whole co-occurance map.

@@

Next we test two state of the arts image repetition detections \cite{Wu2010DL} and \cite{Liu2013GRASP}. \cite{Wu2010DL} use a grid-based method to identify repetitive structures. Multiple grids can be detected from the same image as different repetitive patterns. This method (Figure \ref{fig:prDetection}a, orange) produces overall good detection ( F-score of 0.6465), especially at the low recall end. However it can not identify non-grid repetitions, which results in the poor performance at the high recall end. Liu et al \cite{Liu2013GRASP} uses stochastic search to find correlated features and links them into repetitive objects. This is similar to our building block detection which uses spectral clustering to find correlated detections and then uses graph cut to find object labels for each feature. The key of \cite{Liu2013GRASP} is a ``greedy randomized adaptive search procedure'' that drive the search toward maximum average affinity between the objects. We implement the search algorithm as described in \cite{Liu2013GRASP}, and restrict the search to translational symmetry to avoid over-fitting of the actually translational facade dataset. We found the search often produce less satisfactory detections (Figure \ref{fig:prDetection}a, blue, F-score of 0.6324). One important reason is they do not enforce bijective matching between features of repetitive objects. Although this allows the handling of object deformation, the model still over-fit repetitions that are observed from the front-parallel view. Another reason is the use of \emph{average affinity} as the single optimizing criteria, which biases the search towards movement that removes potential outliers and leads to partial detection. Compare to these methods, our detection (Figure \ref{fig:prDetection}a, red) gives the best F-score (0.7007). Compare to the second best method (\cite{Wu2010DL}) we have significant better performance at the high recall end with only marginal lost on the high precision end.

@@

Here $E_{s}^{pixel}$ is the conventional pixel-based smoothness term as used by \cite{Pritch09ICCV} and \cite{He2012PO}. It penalizes two neighboring labels $a, b$ that creates a seam for adjacent pixels $x, x'$:
%
\begin{equation}
E_{s}^{pixel}(x, x', a, b) = |I(x + s_{a}) - I(x + s_{b})| + |I(x' + s_{a}) - I(x' + s_{b})|
\label{eq:EPixelSmooth}
\end{equation}
%
In addition to it, we introduce two new constraints: the class smoothness cost $E_{s}^{class}$ and the position smoothness cost $E_{s}^{position}$. They are Potts models with different building blocks properties.

@@

\revised{To address this problem, we sample offset labels from statistics of building blocks. In this way both the search space is constructed based on the regularity in the image. This often leads to further improvement of the synthesis results, as shown in Figure \ref{fig:IntermediumSyn} d). Our sampling contains two main steps: It first computes predominant offsets between the same class of building blocks. These offsets are then used as generators to regularly generate input labels for graph cut. Specifically, it works as follows: A probability density map (PDF) is computed by accumulating votes of pairwise building blocks offsets. Only building blocks of the same class are considered in the voting. We then detect local peaks in the PDF using non-maximum suppression. These local peaks were used in previous works as offset labels for image completion, as described in \cite{He2012PO}. Differently, for our task of image retargeting a larger montage must be created to cover the synthesis domain. In theory this can be achieved by recursively sampling new peaks from the PDF. However the number of offsets will be increased by a power function and the search becomes infeasible in practice. To handle this problem, we find predominant offsets and use them as grid generators to efficiently create the montage: the first generator is the strongest peak in the PDF, and the second generator is the next strongest peak that satisfies a minimum angular distance to the first generator. The minimum angular (set to $\frac{\pi}{3}$) requirement de-correlates the two generators so the montage can be efficiently expanded as a 2-D grid. In the pursuit of higher variability in the results, additional generators can be combined with these two to create extra grids. For example, randomness in the synthesis results can be created using a near-regular grid. However, in practice we found a regular grid spanned by two predominate generators trades off well between stability and variability.}

@@

\textbf{Limitations and Future Work:} Our method has a number of limitations, some of which could be addressed in future work. First of all, it is limited to translational building blocks. While the feature and learning pipeline is able to compensate some distortions, strong perspective, scaling, or rotation cannot be handled. We believe that this can be extended quite easily; the main challenge is that we need to replace the global alignment of co-occurrence maps with local alignments that take the coordinate frame of pairwise matches into account. Second, as shown in the pressure test, statistics favors the grid-based detection when the demand of shape accuracy is high. This implies higher level regularity, when observed, should be incorporated to improve our detection. This is important because only high quality detection is able to help later applications. For example, inaccurate detection can only downgrades image synthesis by imposing useless constraints. Further, although we have tried to build tiling grammar using building blocks as discrete elements, the inference of such grammar is combinatorially hard. In many cases our found little or no improvement from the grammar. Here, we could think of including more comprehensive, global relations such as symmetry or hierarchy~\cite{Hu2013PPI}, or we could use the inverse procedural modeling approach in the spirit of \cite{BOKELOHsig2010,Sylvain2010AT} to obtain stronger guarantees for a subset of structures. In summary, conventional pixel-level synthesis has to rely on MRF-based texture generation; while guidance helps, we still observe artifacts and failure cases. A more fundamental understanding of image structure would be necessary to obtain more powerful models.

>>>>

We replace structural priors by the assumption of coherently mapped building blocks, which are related by a common transformation and residual distortions. We discover such structures by relating co-occurrence maps of images features using a spectral embedding, which draws its robustness out of the ability to use the whole \revised{4D (chris: this is in the old paper and I do not understand it now)} matching information in a single optimization for discovering coherently mapped pieces. We evaluate our method on a large benchmark data set of facade images. In comparison to previous methods, both with \cite{Wu2010DL} and without structural priors \cite{LIPMANsig2010,Liu2013GRASP}, we obtain a significant improvement.

@@

\revised{In this paper we restrict the detection to translational building blocks. Having additional degrees of freedom (scaling, rotation, perspective, ... etc) may broaden the scope of applications, but are less important for our purpose of improving MRF for image retargeting/editing. In fact most of the MRF synthesizers, including \cite{Kwatra2005TO}\cite{Simakov2008SV}\cite{Pritch09ICCV}\cite{He2012PO}, use only translations. Additional DoF increases the search space, often leads to suboptimal solutions and computational costs. Restricting to translations is a good balance between model complexity and usability.}

In summary, the main contribution of this paper is a new \revised{unsupervised} approach for discovering \emph{approximate \revised{translational} building blocks} in \revised{real world images with some variations in the appearance of repeated elements}. We develop the idea in the context of an automatic image parsing technique that discovers translational building blocks, and outperforms previous methods in this task. We demonstrate the utility of the discovered building blocks and their geometric relations by applying it to image synthesis, where we can get improvements over unguided methods without sacrificing the fully automatic mode of operation.

@@

\textbf{Symmetry detection} has drawn a considerable amount of interests in both the 2D \cite{Lee2009SR,Wu2010DL} and 3D case \cite{Mitra2006PAA,Pauly2008,LIPMANsig2010,HuangMesh2013}. Most methods perform certain voting, either in the feature space or in the transformation space, and detect symmetries at the local maximums of the vote density. A key for successful detection is to get a good signal to noise ratio for the true repetitions. In feature space, this can be addressed as a feature selection problem. Both global \cite{Wang2008Factor,Agrawal2012RI,Bokeloh2009SD} and local \cite{Leung1996} searches are proposed to find more reliable features, sometimes even constellation of features \cite{Liu2013GRASP}.
%
However, matching is still challenging under strong appearance variation. This problem is partially overcome by voting in the transformation space \cite{Hays2006Texture,Mitra2006PAA}, where spatial mappings between pairwise-matched features are aggregated to amplify the true repetition signal. For lattice-like patterns, detection can be further improved by assuming regular (or near-regular) transformations \cite{Pauly2008,Wu2010DL,Zhao2011TS,Tai2012PF}, see \cite{Lin2006Eva} for a survey. However, this also prohibits detection of irregular patterns.

\revised{In image space, \cite{Wang2008Factor} use small image blocks and affine mappings for compression. Although this model is highly memory efficient, it’s not suitable for guiding retargeting or editing due to over-segmentations, as the relations between the segments may become too complicated for reasoning.} Our method was inspired by the \emph{microtile} decomposition of Kalojanov et al.~\shortcite{KALOJANOVsgp2012}, which characterize generically placed building blocks \revised{in 3D shapes}. However, their method is strictly limited to exact data; even small, numerical errors already cause instability. We also draw inspiration from Lipman et al.~\cite{LIPMANsig2010}, who use spectral clustering to find cliques of pairwise corresponding points in noisy data. Our method extends their model towards cliques of coherently mapped build blocks (rather than points), which improves detection performance.

\textbf{Visual pattern mining:} Supervised, discriminatively trained models (such as \cite{Felzenszwalb2010DPM}) have demonstrated impressive capabilities in structuring images. Unsupervised pattern mining has been addressed by Singh et al.~\shortcite{SINGHeccv2012}. The original method still requires a large background (negative) training set. In our paper, we adapt the basic technique for mining patterns in a single image, where building-block priors provide additional constraints. More recently, great effort has also been made towards fa{\c{c}}ade parsing. Numerous methods \cite{Teboul2011SG,Martinovic2012AT,Bao2013PF} have been proposed to extract semantic layout of building fa{\c{c}}ades. Convincing images can be later synthesized, using methods such as \cite{Dai2013Facade}. However these methods only work on fa{\c{c}}ade and need either supervised learning or manual interaction, while we aim at a fully unsupervised method that generalizes well for a broader range of subjects, so it could \revised{be} directly used to improve existing image synthesis and editing approaches. 
Cheng et al.~\cite{Cheng2010RepFinder} propose a method for finding repetitive image content for use in synthesis applciations. However, in that method, both the mining and synthesis steps again need considerable human supervision. Landes et al.~\cite{Landes2009} find repetitive patterns and re-arrange them in the synthesis image. Here, the use of a simple feature comparison (SIFT with a Euclidean metric) limits the scope of the automatic detections.

\textbf{Texture synthesis} has received a lot of attention in computer graphics, see \cite{Wei2009STAR} for a comprehensive survey. In order to overcome the limitations of the Markov Random Field (MRF) model, various forms of guidance have been employed, for example, using an additional image layer with user annotations \cite{Hertzmann2001IA} or on-the-fly user interaction ~\cite{Barnes2009,Hu2013PPI}. Automating the creation of guidance map is still an on-going research topics, with some success in low level feature maps. For example, Lefebvre and Hoppe~\shortcite{Lefebvre2006ATS} use distance transforms on feature maps to guide the synthesis of high-quality textures with pronounced meso-structure. However, the feature transform cannot structure complex images beyond textures. Rosenberger et al.~\shortcite{Rosenberger2009LSS} extend the idea to irregular textures with non-stationary statistics, such as aged or weathered surfaces. Dishler et al.~\shortcite{Dischler2002} use ``texture particles'' as landmarks, similar to our guidance scheme; however, only textures (with some meso-structure) are synthesized due to limitations in the detection stage. Tiling grammars have been recently employed to guide the placement of discrete elements~\cite{Ma2011DET,Ma2013DET}, however our method handles image data, such as pixels color and class labels, rather than discrete elements. Our application is also related to image retargeting, recomposition and inpainting. Along this direction, various methods have been experimented to avoid local optimal solutions results from the MRFs model. For example, \cite{Simakov2008SV} uses bidirectional matching and a gradual resizing procedure for retain the image structure in retargeting (especially for image shrinking); \cite{Pritch09ICCV,He2012PO} studied pixel offset, and use graph cut to find the optimal pixel assignment for the output image that produces a smooth offset field. Nonetheless, these methods all operate on image pixels, hence can not eliminate structural artefacts. An exception is \cite{Wu2010SS}, which use deformable lattice to retain structure during image resizing. However their method is restricted to images \revised{that have} a global repetition (such as lattice), and is difficult to be used for recomposition. In this paper we will show using additional \revised{building blocks} knowledge is able to improve the performance of the conventional pixel based MRF methods.

@@

\textbf{Learning:} We train a linear support vector for each cluster in one-versus-all fashion \revised{\cite{REF08a}}: One of the clusters provides the positive training set and all others the negative set. \revised{Applying linear SVM yields a weight vector $\bv{w}_i$ that maximizes the margin between the positive cluster and all the negative ones. This weight vector has the same dimension of the HOG feature, and is used to sharpen the later sliding window detection}.

\textbf{Detection:} The detection step updates the dictionary using sliding window detection. For each $8\times 8$-patch of HOG-cells in the image, it computes:
%
\begin{equation}
m_{\textbf{t}_i}(\textbf{x}) = \exp\left(-||\textbf{w}_i\cdot(HOG(\textbf{t}_i) - HOG(\textbf{x}))||_2 \right),
\label{eq:finalMatching}
\end{equation}
%
where $HOG(\bv{x})$ denotes the local $64^2$ pixel HOG patch for image position $\bv{x}$ and median template $\bv{t}_i$, respectively. The result is one \emph{co-occurrence map} for each feature cluster $\bv{t}_i$. Such a map is a scalar image that for each HOG-cell indicates the strength of the match with $\bv{t}_i$; Figure \ref{fig:DL1} compare the co-occurrence maps before and after the learning process.

\textbf{Rebuilding the dictionary:} For the next iteration, we rebuild the the dictionary by using non-maxima suppression on the co-occurrence maps. \revised{Specifically, a scanline operation is used to keep the maximum value in a local window ($\frac{1}{4}$ patch size). In this way the surviving pixels are the local maximums in the oc-currence map.} Matches with a score below a threshold of $\theta = 0.5$ are removed to avoid spurious local maxima. The threshold is intentionally set to a relative low value to allow considerable appearance variation in the repetitive objects. The whole pipeline is then iterated to refine the results.

@@

For an $w \times h$ input image, let $\domain = [0,w/8] \times [0, h/8]$ denote the domain of the HOG-cell representation of the image. We consider a group of \emph{admissible transformations} $\allTransf$ that can be used to move image content (used to relate instances of building blocks). We restrict $\allTransf$ to translations in this paper for \revised{achieving robust unsupervised detection on facade-like patterns from the front view}. Extensions to larger groups (such as similarity transforms, homographies) \revised{might be} possible but left for future work.

@@

\begin{algorithm}
\caption{Image \revised{Parsing}}\label{alg:ImageParsing}
\begin{algorithmic}[1]
\Require{Input image $I$, Maximum number of iteration $N$ for dictionary initialization, maximum number of iteration $M$ for discriminative learning}
\For{$i \gets 1 \textrm{ to } N$}

@@

\subsubsection{Co-occurrence clustering}

In order to address problem (i), finding the transformations, we consider the collection of all 2D slices of the 4D matching function $m$. Consistently with Equation~\ref{eq:finalMatching}, we define the \emph{co-occurrence map} of the feature at point $\vecp \in \domain$ as:
%
\begin{equation}
m_{\vecp}(\vecx) := m(\vecp, \vecx)
\label{eq:corr-map}
\end{equation}
%
This is a simple scalar image, depiciting the spatially-varying strength of match against the feature at image position $\vecp$. If two image positions $\vecp$ and $\vecq$ are part of the same building block, they will have related co-occurrence maps $\corrMap_\vecp,\corrMap_\vecq$ (Figure~\ref{fig:coOccurranceDetection}). The following holds for any point in any of the instances of the building blocks, which makes the method particularly robust:
In absence of noise, the co-occurrence maps of all points on the same building block type will be exact translationally shifted copies of each other. Even in the noisy case, we can expect the images to still resemble each other. Because we obtain an image for every point on a building block, we have a large amount of information we can integrate to even detect weak signals in very noisy and unreliable correspondence information: By comparing the whole image we are able to drastically reduce the noise of the pixel-wise matching function, and clustering the space of all such images can further detect weak patterns. This is the key property for the robustness of our method, and explains the favorable performance in practice. Unlike previous transformation voting methods~\cite{Mitra2006PAA}, transformations from different instances do not mix and pollute the voting space, and spectral methods are improved by being able to utilize all instance information simultaneously rather than corresponding point orbits.

To find clusters of such related co-occurrence maps, we employ a spectral clustering algorithm, which has a global view of all pairwise relations. We first compute the normalized cross-correlation (denoted by $\otimes$) of all pairs of co-occurrence maps $\corrMap_{p},\corrMap_{q}$ to find and score their best translational alignment. We then build a dissimilarity matrix $\textbf{D}$ where
%
\begin{equation}
\textbf{d}_{p, q} = \textbf{d}_{p, q} = 1 - \corrMap_{p} \otimes \corrMap_{q} \text{ for all } p,q \in K\text{.}
\label{eq:distanceMatrix}
\end{equation}
%
We now reconstruct a low dimensional embedding using classical (spectral) multidimensional scaling, where similar co-occurrence maps are located close to each other. We then extract modes of this embedding using meanshift clustering (with bandwidth 0.5), which result in $Q$ clusters ($Q \leq K$). We only keep the median point in each cluster to represent the modes in an outlier-robust way. Figure \ref{fig:SpectralClustering} shows an example of spectral clustering based on co-occurrence maps and compare the result with spectral clustering based on HoG feature distance. By spectral embedding the co-occurrence maps (right), our algorithm is able to group together parts of the same type of building block. For example the word A and B have very different visual appearance but are highly correlated by their co-occurrence maps. In contrast, spectral embedding the HoG features (middle) will falsely group visually similar patches that do not belong the same building block, for example, word B and C.

Each cluster in the embedding is essentially \revised{a list of co-occurrence maps. We use the co-occurrence map of the cluster median to create a clique for distributing instances of a particular type of building blocks.} These cliques are encoded as binary masks in image space by applying the same thresholding and non-maxima supression to the \revised{median} co-occurrence maps as described in the second last paragraph of Section \ref{sec:IterativeDL}. In these masks, one pixel is set to one for each local maxima and all other cells have value zero. Knowing the \revised{distribution of the building blocks}, we next identify the exact shapes of each building block instance.

Finally, we can easily integrate the learned dictionaries computed in step 1 by computing and embedding the co-occurrence maps only for the dictionary entries rather than for all image features. This dramatically reduces the costs for spectral embedding over a naive all-pairs approach and additionally profits from the pre-sharpened detectors.

%It is important to note that our clustering is also very different from symmetry factored embedding~\cite{LIPMANsig2010}, which considers only equality of points, not of whole co-occurrence map.

@@

Next we test two state of the arts image repetition detections \cite{Wu2010DL} and \cite{Liu2013GRASP}. \cite{Wu2010DL} use a grid-based method to identify repetitive structures. Multiple grids can be detected from the same image as different repetitive patterns. This method (Figure \ref{fig:prDetection}a, orange) produces overall good detection ( F-score of 0.6465), especially at the low recall end. However it can not identify non-grid repetitions, which results in the poor performance at the high recall end. Liu et al \cite{Liu2013GRASP} uses stochastic search to find correlated features and links them into repetitive objects. This is similar to our building block detection which uses spectral clustering to find correlated detections and then uses graph cut to find object labels for each feature. The key of \cite{Liu2013GRASP} is a ``greedy randomized adaptive search procedure'' that drive the search toward maximum average affinity between the objects. We implement the search algorithm as described in \cite{Liu2013GRASP}, and restrict the search to translational symmetry to avoid over-fitting of the actually translational facade dataset. We found the search often produce less satisfactory detections (Figure \ref{fig:prDetection}a, blue, F-score of 0.6324). One important reason is they do not enforce bijective matching between features of repetitive objects. Although this allows the handling of object deformation, the model still over-fit repetitions that are observed from the front-parallel view. Another reason is the use of \emph{average affinity} as the single optimizing criteria, which biases the search towards movement that removes potential outliers and leads to partial detection. \revised{As \cite{Liu2013GRASP} uses a dictionary of features to initialize its research, it can potentially over-fit the initial dictionary. For fair comparison we re-run the algorithm for 30 times with different initializations and use our model selection to merge the results. Doing so raised GRASP’s F-score to 0.6612.}

Compare to these methods, our detection (Figure \ref{fig:prDetection}a, red) gives the best F-score (0.7007). Compare to the second best method (\cite{Wu2010DL}) we have significant better performance at the high recall end with only marginal lost on the high precision end. \revised{This means we are able to find more patterns, especially those do not form a regular grid, with little lost on the overall accuracy.} \revised{Compare to the third best method (\cite{Liu2013GRASP}) we are consistently better for detecting translational patterns for using a less greedy research algorithm (spectral clustering) and for enforcing bijective matching for cutting out building blocks. This also means our method is more rigid and does not handle perspective, rotational and occluded patterns as \cite{Liu2013GRASP} does.  Nonetheless, for applications such as image retargeting, it is often risky to introduce too many degrees of freedom for avoiding local optimal search and high computational cost. For this reason we leave the detection of more challenging cases as future work and do not investigate any further in this paper.}

@@

Here $E_{s}^{pixel}$ is the conventional pixel-based smoothness term as used by \cite{Pritch09ICCV} and \cite{He2012PO}. It penalizes two neighboring labels $a, b$ that creates a seam for adjacent pixels $x, x'$:
%
\begin{equation}
E_{s}^{pixel}(x, x', a, b) = |I(x + s_{a}) - I(x + s_{b})| + |I(x' + s_{a}) - I(x' + s_{b})|
\label{eq:EPixelSmooth}
\end{equation}
%
In addition to it, we introduce two new constraints: the class smoothness cost $E_{s}^{class}$ and the position smoothness cost $E_{s}^{position}$. They are Potts models \revised{\cite{BOYKOVpami2001}} with different building blocks properties. \revised{Such model has zero cost for any $a = b$. In this way it encourages labellings consisting of several regions where pixels in the same region have equal labels.}

@@

\revised{To address this problem, we sample offset labels from statistics of building blocks. In this way both the search space is constructed based on the regularity in the image. This often leads to further improvement of the synthesis results, as shown in Figure \ref{fig:IntermediumSyn} d). Our sampling contains two main steps: It first computes predominant offsets between the same class of building blocks. These offsets are then used as generators to regularly generate input labels for graph cut. Specifically, it works as follows: A probability density map (PDF) is computed by accumulating votes of pairwise building blocks offsets. Only building blocks of the same class are considered in the voting. We then detect local peaks in the PDF using non-maximum suppression. These local peaks were used in previous works as offset labels for image completion, as described in \cite{He2012PO}. Differently, for our task of image retargeting a larger montage must be created to cover the synthesis domain. In theory this can be achieved by recursively sampling new peaks from the PDF. However the number of offsets will be increased by a power function and the search becomes infeasible in practice. To handle this problem, we find predominant offsets and use them as grid generators to efficiently create the montage: the first generator is the strongest peak in the PDF, and the second generator is the next strongest peak that satisfies a minimum angular distance to the first generator. The minimum angular (set to $\frac{\pi}{3}$) requirement de-correlates the two generators so the montage can be efficiently expanded as a 2-D grid. In the pursuit of higher variability in the results, additional generators can be used to create extra grids. However, in practice we found a regular grid spanned by two predominate generators trades off well between stability and variability.}

@@

\textbf{Limitations and Future Work:} Our method has a number of limitations, some of which could be addressed in future work. First of all, it is limited to translational building blocks. While the feature and learning pipeline is able to compensate some distortions, strong perspective, scaling, rotation or cannot be handled. We believe that this can be \revised{extended in the future}; the main challenge is that we need to replace the global alignment of co-occurrence maps with local alignments that take the coordinate frame of pairwise matches into account. Second, as shown in the pressure test, statistics favors the grid-based detection when the demand of shape accuracy is high. This implies higher level regularity, when observed, should be incorporated to improve our detection. \revised{Deformation in geometry, color, shadow/lighting are also problematic. While small deformations and occlusion can be handled by statistics based low level features the co-occurrence analysis, sever ones breaks the definition of building blocks. In such cases supervision might be useful for achieving further flexibility at both the feature and the building block levels.} This is important because only high quality detection is able to help later applications. For example, inaccurate detection can only downgrades image synthesis by imposing useless constraints. Further, although we have tried to build tiling grammar using building blocks as discrete elements, the inference of such grammar is combinatorially hard. In many cases our found little or no improvement from the grammar. Here, we could think of including more comprehensive, global relations such as symmetry or hierarchy~\cite{Hu2013PPI}, or we could use the inverse procedural modeling approach in the spirit of \cite{BOKELOHsig2010,Sylvain2010AT} to obtain stronger guarantees for a subset of structures. In summary, conventional pixel-level synthesis has to rely on MRF-based texture generation; while guidance helps, we still observe artifacts and failure cases. A more fundamental understanding of image structure would be necessary to obtain more powerful models.
